%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.2 (3/28/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Modified by:
% Daniel L Marks <xleafr@gmail.com> 3/28/2015
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You can have multiple style options the legal options ones are:
%
%   centered:	the name and address are centered at the top of the page 
%				(default)
%
%   line:		the name is the left with a horizontal line then the address to
%				the right
%
%   overlapped:	the section titles overlap the body text (default)
%
%   margin:		the section titles are to the left of the body text
%		
%   11pt:		use 11 point fonts instead of 10 point fonts
%
%   12pt:		use 12 point fonts instead of 10 point fonts
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin]{res}  

% Default font is the helvetica postscript font
\usepackage{helvet}
\usepackage{hyperref}

% Increase text height
\textheight=700pt

\begin{document}

%-------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%-------------------------------------------------------------------------------
\name{\huge{Pedro Vaz Pimenta}}

% Note that addresses can be used for other contact information:
% -phone numbers
% -email addresses
% -linked-in profile

\address{\\ pedro.vaz.pimenta@alumni.usp.br \\Phone/WhatsApp: +55 16 99228-3451\\ www.linkedin.com/in/pedro-vaz-pimenta/  \\ github.com/pedrovazpimenta}
\address{\\ Address: Rua Sexto Patelli, 131 \\ Campo Limpo Paulista \\ S\~ao Paulo  CEP 13231-360. \\ Available for work in:  S\~ao Paulo and near cities}

\address{\\}


% Uncomment to add a third address
%\address{Address 3 line 1\\Address 3 line 2\\Address 3 line 3}
%-------------------------------------------------------------------------------

\begin{resume}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{OBJECTIVE}
{\sl Jobs in Data Science and related fields. }

\section{EDUCATION}
\textbf{University of S\~ao Paulo (USP) - IME}, S\~ao Paulo\\
{\sl BSc in Mathematics} \\
Feb, 2019 - Dec, 2021.
 

%-------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{TECHNICAL\\SKILLS}

\textbf{Programming : } Python, MySQL, R, C/C++, \LaTeX , ProLog/ProbLog.
\\
\textbf{ Languages : } Portuguese(native), English(Advanced - C1). 
\\
\textbf{Tools : } Pandas, SpaCy, Nltk, Scikit-Learn, PyTorch, Keras/TensorFlow, OpenCV, NumPy, Google Cloud Platform (GCP), Azure (Cloud and DevOps), Docker, OpenAI API, LangChain, Celery, Redis, RediSearch, OpenSearch, Tika. 
\\
\textbf{General :} Data Structures, Databases, Algorithms, Object Oriented Programming, Descriptive Statistics, Probability Theory, Statistical Inference, Numerical Methods, Mathematical Modeling, Machine Learning, Microsoft Office, Agile Methods, Scrum, Kanban, Natural Language Processing, Named-entity Recognition (NER), Text Classification, Prompt Engineering, Vector Databases, Image Segmentation, Image Classification.

%-------------------------------------------------------------------------------
% Modify the format of each position
\begin{format}
\title{l}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------

\section{EXPERIENCE}

\textbf{Data Scientist at Poatek \hfill{Dec 2021 - Present}\\}
\normalfont{Working in multiple client projects with:

- Natural Language Processing (NLP) for Sensitive Data Extraction (such as PII and PHI) and Anonymization on texts using Named Entity Recognition based on rules and Deep Learning models. My work also includes text classification and confidence/risk analysis for extractions.

- Knowledge bases for Large Language Models using KNN Search in Vector Databases in order to create a more accurate ChatGPT using Prompt Engineering and Few Shot Learning. 

- Computer Vision: image processing, models and pipelines for document detection, classification and OCR.} 

\textbf{Private Math Teacher \hfill{Jan 2016 - Jul 2021}\\}
\normalfont{Private tutoring for students of all levels with difficulties in mathematics.} \\


\section{RELEVANT\\COURSES}
\par

\normalfont{\textbullet{} Introduction to Machine Learning\\ }
\normalfont{\textbullet{} Understanding and Visualizing Data with Python \\}
\normalfont{\textbullet{} Introduction to Structured Query Language (SQL)\\}
\normalfont{\textbullet{} Introduction to Data Science in Python }
\normalfont{\textbullet{} Probability and Statistics\\}
\normalfont{ \textbullet{} Natural Language Processing }
\normalfont{ \textbullet{} Linear and Nonlinear Optimization \\}
\normalfont{\textbullet{} Algorithms and Computer Programming }




\section{INTERESTS}
\par

\normalfont{\textbullet{} Data Science }
\normalfont{\textbullet{} Data Analysis }
\normalfont{\textbullet{} Big Data}
\normalfont{\textbullet{} Deep Learning \\}
\normalfont{ \textbullet{} Pattern Recognition } 
\normalfont{\textbullet{} Data Visualization \\}
\normalfont{\textbullet{} Natural Language Processing and Large Language Models}
 

%-------------------------------------------------------------------------------


\end{resume}
\(\)\end{document}
